Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-12 paperIEEE.tex
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@124 db7c848b-7755-4df2-b763-8796797afa52

@@

\subsubsection{Implicit Load Balancing}

The package equalizer allows to adjusts the implicit load balancing that results from rendering clients pulling work packages, i.e., tiles and chunks, from a central queue on the server. It is implemented as \textsf{tile\_equalizer} and \textsf{chunk\_equalizer}, respectively, and changes the affinity of work packages to individual nodes, based on an affinity model specified to the equalizer. In~\cite{SPEP:16}, we explore this approach in more detail.

>>>>

\subsubsection{Dynamic Work Packages}

The package equalizer allows to adjusts the implicit load balancing that results from rendering clients pulling work packages, i.e., tiles and chunks, from a central queue on the server. It is implemented as \textsf{tile\_equalizer} and \textsf{chunk\_equalizer}, respectively, and changes the assignment of work packages to individual nodes, based on an affinity model specified to the equalizer. In~\cite{SPEP:16}, we explore this approach in more detail.

@@
